Reducing iptables configuration complexity using chains

### 2014-05-08 iptables/presentation.tex
highlight ip6tables
use term 'custom chains' everywhere
mention better performance

    \textbf{This is possible with chains!}

@@

    \frametitle{Introducing chains}
    Create the chain and add the rules

@@

      \item the list of IP addresses in the custom chain is reused for both ports, so they have to be defined only once.

@@

      \item a better overview of the firewall rules.

@@

  \begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
      \item use ESTABLISHED state to reduce number of rules
      \item using chains makes your rules easier readable and maintainable
      \item chains can be reused for several rules
      \item chains can be chained together
      \item faster, because it only jumps to a chain when a rule matches
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    \vfill
    Contact
    \begin{itemize}
      \item Blog : \href{http://ruleant.blogspot.com/}{http://ruleant.blogspot.com}
      \item Twitter : \href{https://twitter.com/dcadriaenssens}{@dcadriaenssens}
    \end{itemize}
  \end{frame}
  \begin{frame}
    \frametitle{IPv6}
    Configuration is the same for IPv4, use ip6tables :
    \begin{example}
      \small{ip6tables -P INPUT DROP\\
      ip6tables -P OUTPUT ACCEPT\\
      ip6tables -A INPUT -i lo -j ACCEPT \# allow local traffic\\
      ip6tables -A INPUT -p icmp -j ACCEPT \# allow ping, etc\\
      ip6tables -A INPUT -m state \dd state ESTABLISHED -j ACCEPT\\
      ip6tables -A INPUT -m state \dd state RELATED -j ACCEPT}
    \end{example}
    Even if IPv4 rules are set, IPv6 has to be configured seperately, otherwise the defaults apply.
  \end{frame}
  \begin{frame}
    \frametitle{IPv6 only day}
    \begin{columns}
      \begin{column}{5cm}
        \includegraphics[scale=.3]{pictures/World_IPv6_launch_badge_512.png}
      \end{column}
      \begin{column}{6cm}
        \textbf{June 6th 2014}\\

>>>>

    \textbf{This is possible with custom chains!}

@@

    \frametitle{Introducing custom chains}
    Create the custom chain and add the rules

@@

      \item the list of IP addresses in the custom chain is reused for both ports, so they have to be defined only once

@@

      \item a better overview of the firewall rules
      \item better performance : the rules in the custom chain are only checked if that chain is accessed

@@

  \begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
      \item use ESTABLISHED state to reduce number of rules
      \item using chains makes your rules easier readable and maintainable
      \item chains can be reused for several rules
      \item chains can be chained together
      \item faster, because it only jumps to a chain when a rule matches
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    \vfill
    Contact
    \begin{itemize}
      \item Blog : \href{http://ruleant.blogspot.com/}{http://ruleant.blogspot.com}
      \item Twitter : \href{https://twitter.com/dcadriaenssens}{@dcadriaenssens}
    \end{itemize}
  \end{frame}
  \begin{frame}
    \frametitle{IPv6}
    Configuration is the same for IPv4, use \textit{ip6tables} :
    \begin{example}
      \small{ip6tables -P INPUT DROP\\
      ip6tables -P OUTPUT ACCEPT\\
      ip6tables -A INPUT -i lo -j ACCEPT \# allow local traffic\\
      ip6tables -A INPUT -p icmp -j ACCEPT \# allow ping, etc\\
      ip6tables -A INPUT -m state \dd state ESTABLISHED -j ACCEPT\\
      ip6tables -A INPUT -m state \dd state RELATED -j ACCEPT}
    \end{example}
    Even if IPv4 rules are set, IPv6 has to be configured seperately, otherwise the defaults apply.
  \end{frame}
  \begin{frame}
    \frametitle{IPv6 only day}
    \begin{columns}
      \begin{column}{5cm}
        \includegraphics[scale=.3]{pictures/World_IPv6_launch_badge_512.png}
      \end{column}
      \begin{column}{6cm}
        \textbf{June 6th 2014}\\
